% =====================================================================
% Note on: Constant Maturity Asset Swap Convexity Correction
% Mario Pucci (Banca IMI), 2012 — ssrn:1961545
% =====================================================================
\documentclass[11pt,a4paper]{article}

\newcommand{\papertag}{pucci\_2012\_cmasw}

\input{../_common/preamble}
\input{../_common/notation}

\title{Note on: \emph{Constant Maturity Asset Swap Convexity Correction}\\
       \large Mario Pucci (Banca IMI), 2012}
\author{Reading notes}
\date{\today}

\begin{document}
\maketitle

% =====================================================================
\section*{Metadata}
\begin{tabular}{@{}p{3.5cm}p{11cm}@{}}
\toprule
Title           & Constant Maturity Asset Swap Convexity Correction \\
Author          & Mario Pucci (Banca IMI, Milan) \\
Date            & 27 February 2012 \\
Source          & \href{https://ssrn.com/abstract=1961545}{ssrn:1961545} \\
Local file      & \texttt{papers/pucci\_2012\_cmasw/ssrn1961545.pdf} \\
Tags            & \texttt{cmasw}, \texttt{asset-swap}, \texttt{convexity},
                  \texttt{linear-swap-rate}, \texttt{displaced-lognormal}, \texttt{correlation} \\
Date read       & \today \\
\bottomrule
\end{tabular}

% =====================================================================
\section*{One-paragraph summary}
The paper prices an ``ASW-let'' --- a payoff that pays a fixing of the
forward asset swap spread of a reference bond at a future date --- as
the constant-maturity analogue of a CMS-let. The forward ASW spread
$R^{asw}_t$ is shown to be a ratio of risk-free tradables and so a
martingale under the swaption measure $A_t$. Under the
Hunt--Kennedy/Pelsser one-factor linear swap-rate model
($D_{T_0 U}/A_{T_0} = \alpha + \beta_U R^{swp}_{T_0}$), the convexity
correction reduces to a single covariance
$\mathbb{E}^N_0[R^{asw}_{T_0} R^{swp}_{T_0}]$ between the ASW spread
and the swap rate. With both rates modelled as displaced-lognormal
(allowing negative ASW spreads --- relevant for premium bonds), the
correction admits a clean closed form. A numerical example calibrated
to plausible Italian sovereign levels (ASW = 490~bp, swap = 4.29\%, 5Y)
gives convexity corrections in the range $-0.19\%$ to $+0.37\%$
depending on correlation $\rho \in \{-90\%, \ldots, +90\%\}$ and ASW
vol $\sigma^{asw} \in \{20\%, 30\%, 50\%\}$.

% =====================================================================
\section{Setup and notation}

\begin{tabular}{@{}p{3cm}p{3.5cm}p{8.5cm}@{}}
\toprule
Paper                   & House                        & Meaning \\
\midrule
$R^{asw}_{t T_0}$       & $R^{asw}_t$                  & Forward asset swap spread at $t$ for ASW starting at $T_0$ \\
$R^{swp}_t$             & $R^{swp}_t$                  & Forward swap rate at $t$, same tenor as the ASW \\
$B_t$                   & $\Bond{t}{\cdot}$            & Reference bond price process \\
$B^{\text{risk-free}}_t$ & ---                         & Hypothetical risk-free version of the same bond (benchmark) \\
$D_{tT}$                & $\Disc{t}{T}$                & Risk-free discount factor \\
$A_t$                   & $\Ann{t}$                    & Risk-free annuity, $\sum_{i} \alpha_i \Disc{t}{T_i}$ \\
$N_t$                   & $\Numer{t}$                  & Numeraire (paper picks $N = A$) \\
$T_0, T_p$              & $T_0, T_p$                   & Fixing date, payment date ($T_p \ge T_0$, usually $T_p = T_1$) \\
$\alpha, \beta_U$       & $\alpha, \beta_U$            & Linear-model coefficients \\
$\sigma^{swp}, \sigma^{asw}$ & ---                     & Displaced-lognormal vols \\
$a^{swp}, a^{asw}$      & ---                          & Displacements \\
$\rho$                  & $\rho$                       & Instantaneous correlation between the two driving BMs \\
$CC$                    & ---                          & Convexity correction (definition in eq.~\ref{eq:cmasw-cc-def}) \\
\bottomrule
\end{tabular}

% =====================================================================
\section{Key equations}

\paragraph{Forward ASW spread (definition):}
\begin{equation}\label{eq:cmasw-asw-def}
  R^{asw}_{t T_0} \;\equiv\; \frac{B^{\text{risk-free}}_t - B_t}{\Ann{t}}.
\end{equation}
\textit{Says:} the forward ASW spread is the gap between a risk-free
benchmark bond and the actual bond, expressed as a per-period
annuity-weighted rate. As a ratio of tradable assets, it is a
martingale under the swaption measure (with numeraire $\Ann{}$).

\paragraph{Convexity correction (definition):}
\begin{equation}\label{eq:cmasw-cc-def}
  CC \;\equiv\; \frac{\Numer{0}}{\Disc{0}{T_p}}\, \E^N_0\!\left[ R^{asw}_{T_0}\, \Disc{T_0}{T_p} / \Numer{T_0} \right] \;-\; R^{asw}_0.
\end{equation}
\textit{Says:} the correction is the difference between the forward
price of an $R^{asw}_{T_0}$ payment at $T_p$ and the
``no-volatility'' value $R^{asw}_0 \Disc{0}{T_p}$.

\paragraph{Linear swap-rate model.}
\begin{equation}\label{eq:cmasw-linearG}
  \frac{\Disc{T_0}{U}}{\Ann{T_0}} \;=\; G_U(R^{swp}_{T_0}) \;=\; \alpha + \beta_U R^{swp}_{T_0},
\end{equation}
for all $U \in \{T_p, T_1, \ldots, T_n\}$, with
\begin{equation}\label{eq:cmasw-calib}
  \alpha \;=\; \frac{1}{\sum_{i=1}^n \alpha_i}, \qquad
  \beta_U \;=\; \frac{\Disc{0}{U}/\Ann{0} - \alpha}{R^{swp}_0}.
\end{equation}
\textit{Says:} same calibration as in Pucci's CMT paper; here the
swap rate plays the role that $\Rcmt$ played there.

\paragraph{Linear-swap ASW convexity correction} (Proposition 1):
\begin{equation}\label{eq:cmasw-cc-prop}
  CC \;=\; \left(1 - \frac{\Ann{0}\, \alpha}{\Disc{0}{T_p}}\right) \left( \frac{\E^N_0[R^{asw}_{T_0} R^{swp}_{T_0}]}{R^{swp}_0} - R^{asw}_0 \right).
\end{equation}
\textit{Says:} the correction is the product of (i) a discount-curve
geometric factor and (ii) the covariance excess of
$R^{asw}_{T_0} R^{swp}_{T_0}$ over its deterministic value. Sign
follows the sign of correlation when both rates are martingales.

\paragraph{Displaced-lognormal dynamics:}
\begin{align}
  \frac{\dd R^{swp}_t}{R^{swp}_t + a^{swp}} &= \sigma^{swp}\, \dd W^{swp}_t, \label{eq:cmasw-dl-swp}\\
  \frac{\dd R^{asw}_t}{R^{asw}_t + a^{asw}} &= \sigma^{asw}\, \dd W^{asw}_t, \label{eq:cmasw-dl-asw}\\
  \rho &= \dd\langle W^{swp}, W^{asw}\rangle_t / \dd t.
\end{align}
\textit{Says:} the displacement $a$ allows the rate to become
negative; this matters here because asset-swap spreads can be
negative on premium bonds (mentioned in the introduction).

\paragraph{Cross-expectation under displaced-lognormal} (eq.~(7) in body):
\begin{equation}\label{eq:cmasw-cross-exp}
  \begin{split}
    \E^N_0[R^{swp}_{T_0} R^{asw}_{T_0}]
    \;=\; & (R^{swp}_0 + a^{swp})(R^{asw}_0 + a^{asw})\, \exp(\sigma^{swp}\sigma^{asw}\, \rho\, T_0) \\
    & - a^{swp}(R^{asw}_0 + a^{asw}) - a^{asw}(R^{swp}_0 + a^{swp}) + a^{swp} a^{asw}.
  \end{split}
\end{equation}
\textit{Says:} closed-form cross-moment in the DL model. Substitute
into \eqref{eq:cmasw-cc-prop} for the full $CC$.

\paragraph{Pure lognormal limit} (Corollary 3, $a^{swp} = a^{asw} = 0$):
\begin{equation}\label{eq:cmasw-cc-lognormal}
  CC \;=\; R^{asw}_0\, \left(1 - \frac{\Ann{0}\, \alpha}{\Disc{0}{T_p}}\right)\, \bigl( \exp(\sigma^{swp}\, \sigma^{asw}\, \rho\, T_0) - 1 \bigr).
\end{equation}
\textit{Says:} the cleanest case. The convexity correction is
proportional to $R^{asw}_0$ and to the correlation-weighted
covariance factor; sign of $CC$ equals sign of $\rho$ (with the
geometric prefactor positive in the usual regime $\Ann{0}\, \alpha < \Disc{0}{T_p}$).

\paragraph{Validity conditions for displaced-diffusion} (Remark 2):
\begin{equation}\label{eq:cmasw-dl-validity}
  R^{asw}_0 > -a^{asw} \quad \text{(DL lognormal)} \qquad \text{or} \qquad 0 < R^{asw}_0 < -a^{asw} \quad \text{(DL anti-lognormal)},
\end{equation}
and similarly for $R^{swp}$.

% =====================================================================
\section{Derivations \& commentary}

\begin{commentary}
The headline move is the same as in the CMT paper: identify
$R^{asw}$ with a ratio of tradables (here just on the risk-free curve,
no defaultable processes needed). Under the swaption measure with
numeraire $A$, $R^{asw}$ is a martingale and CMS machinery transfers
directly. The catch is that the dynamics of $R^{asw}$ and $R^{swp}$
must be modelled jointly --- $CC$ depends on their
\emph{cross-moment}, not just on individual variances. So this is a
correlation product, with all the calibration problems that implies.
\end{commentary}

\begin{commentary}
The choice of displaced-lognormal instead of plain lognormal is
operationally important: ASW spreads on premium bonds (where the
bond's coupon exceeds market levels) can be \emph{negative}. The
paper notes that this used to be the case for treasuries when
interbank deposits were perceived less risk-free. A pure lognormal
process forbids this, so DL is the safer modelling default even when
$R^{asw}_0 > 0$ today.
\end{commentary}

\begin{commentary}
The paper's $\S 8$ honestly enumerates the model's weaknesses:
\textbf{(i)} the linear-$G_U$ assumption may not be realistic for
long-tenor bonds (richer functional forms in Hagan's Convexity
Conundrums exist); \textbf{(ii)} the ASW vol is hard to imply since
liquid ASW options don't exist --- historical estimation is needed,
possibly supplemented by bond-option quotes; \textbf{(iii)} static
replication a la Hagan doesn't trivially apply to ASW-let because
the swaption-measure formula contains \emph{both} $R^{asw}_{T_0}$
and $R^{swp}_{T_0}$ explicitly; \textbf{(iv)} correlation is also
not market-implied.
\end{commentary}

\begin{commentary}
The forward ASW package embeds a forward position on the underlying
bond. Forward repo on sovereigns is thin; the paper notes that for
issuers with a deep curve (FR, IT, BE, DE) the forward bond can be
synthesised by coupon-stripping or bootstrapping a zero curve.
\end{commentary}

% =====================================================================
\section{Validation}

\begin{validation}
This is a \emph{specification} of mathematical objects the paper
defines and the numerical values they should take. It says nothing
about how those objects are implemented or invoked.

\textbf{Quantities the paper defines:}
\begin{itemize}[noitemsep]
  \item Forward ASW spread $R^{asw}_{t T_0}$ via
        \eqref{eq:cmasw-asw-def}.
  \item Convexity correction $CC$ via \eqref{eq:cmasw-cc-def}.
  \item Linear-model coefficients $\alpha, \beta_U$ via
        \eqref{eq:cmasw-calib}.
  \item Linear-swap closed-form $CC$ via \eqref{eq:cmasw-cc-prop}.
  \item Cross-expectation under DL dynamics
        \eqref{eq:cmasw-cross-exp}, and its lognormal limit
        \eqref{eq:cmasw-cc-lognormal}.
\end{itemize}

\textbf{Canonical numerical case} (paper Tables 1, 4, 5; section 7):
\begin{itemize}[noitemsep]
  \item Reference: Italian sovereign bond schedule (paper Tab.~4);
        $T_p = 08/02/2017$ (one specific period).
  \item Forward swap rate $R^{swp}_0 = 4.29\%$ (matched to discount
        curve, Tab.~5).
  \item Forward ASW spread $R^{asw}_0 = 490$~bp (sovereign-flavoured).
  \item Forward swap-rate vol $\sigma^{swp} = 30\%$.
  \item Tested grid: $\sigma^{asw} \in \{20\%, 30\%, 50\%\}$,
        $\rho \in \{-90\%, -50\%, 0\%, +50\%, +90\%\}$.
\end{itemize}

\textbf{Expected numerical values} (Table 2 of the paper, pure-lognormal $CC$):

\smallskip
\begin{tabular}{@{}lrrrrr@{}}
\toprule
$\sigma^{asw} \backslash \rho$ & $-90\%$ & $-50\%$ & $0\%$ & $+50\%$ & $+90\%$ \\
\midrule
$20\%$ & $-0.09\%$ & $-0.05\%$ & $0.00\%$ & $+0.06\%$ & $+0.12\%$ \\
$30\%$ & $-0.13\%$ & $-0.08\%$ & $0.00\%$ & $+0.10\%$ & $+0.19\%$ \\
$50\%$ & $-0.19\%$ & $-0.12\%$ & $0.00\%$ & $+0.18\%$ & $+0.37\%$ \\
\bottomrule
\end{tabular}
\smallskip

\textit{Sensitivity to ASW slope} (paper Table 3, DL skew impact):

\smallskip
\begin{tabular}{@{}lrrrrr@{}}
\toprule
$\sigma^{asw} \backslash \rho$ & $-90\%$ & $-50\%$ & $0\%$ & $+50\%$ & $+90\%$ \\
\midrule
$20\%$ & $0.02\%$ & $0.01\%$ & $0.00\%$ & $0.01\%$ & $0.03\%$ \\
$30\%$ & $0.05\%$ & $0.02\%$ & $0.00\%$ & $0.02\%$ & $0.08\%$ \\
$50\%$ & $0.11\%$ & $0.04\%$ & $0.00\%$ & $0.07\%$ & $0.28\%$ \\
\bottomrule
\end{tabular}
\smallskip

\textbf{Equation $\leftrightarrow$ quantity map:}

\smallskip
\begin{tabular}{@{}p{2.8cm}p{3.8cm}p{6.2cm}@{}}
\toprule
Paper eq.                     & Symbol                          & Quantity \\
\midrule
\eqref{eq:cmasw-asw-def}      & $R^{asw}_{t T_0}$               & forward ASW spread as ratio of risk-free tradables \\
\eqref{eq:cmasw-cc-def}       & $CC$                            & convexity correction (definition) \\
\eqref{eq:cmasw-linearG}--\eqref{eq:cmasw-calib} & $\alpha, \beta_U$ & linear swap-rate model coefficients \\
\eqref{eq:cmasw-cc-prop}      & $CC$                            & closed-form CC under linear model \\
\eqref{eq:cmasw-cross-exp}    & $\E^N_0[R^{swp}_{T_0} R^{asw}_{T_0}]$ & DL cross-expectation \\
\eqref{eq:cmasw-cc-lognormal} & $CC$ (lognormal limit)          & pure lognormal closed form \\
\bottomrule
\end{tabular}
\smallskip

\textbf{Invariants and identities to verify:}
\begin{enumerate}[noitemsep]
  \item \emph{Reproduction of Table 2}: the lognormal closed form
        \eqref{eq:cmasw-cc-lognormal} with $R^{asw}_0 = 490$~bp,
        $\sigma^{swp} = 30\%$, $T_0 \approx 5$Y, and the appropriate
        $\Ann{0}\alpha/\Disc{0}{T_p}$ factor should reproduce the
        $\sigma^{asw} \times \rho$ grid above to within $0.01\%$.
  \item \emph{Linear-calibration consistency}: $\alpha + \beta_{T_p} R^{swp}_0 = \Disc{0}{T_p}/\Ann{0}$
        and the sum $\sum_{i} \alpha_i (\alpha + \beta_{T_i} R^{swp}_0) = 1$
        hold by construction.
  \item \emph{DL $\to$ lognormal limit}: as $a^{swp}, a^{asw} \to 0$,
        \eqref{eq:cmasw-cross-exp} reduces to
        $(R^{swp}_0)(R^{asw}_0)\exp(\sigma^{swp}\sigma^{asw}\rho T_0)$,
        and the full CC reduces to \eqref{eq:cmasw-cc-lognormal}.
  \item \emph{Sign of $CC$}: under lognormal dynamics and the typical
        regime $\Ann{0}\alpha < \Disc{0}{T_p}$, the sign of $CC$
        equals the sign of $\rho$.
  \item \emph{Vanishing at zero vol}: $CC = 0$ whenever
        $\sigma^{swp} \sigma^{asw} = 0$ (lognormal limit), or
        whenever both rates are independent ($\rho = 0$ in lognormal).
  \item \emph{DL validity}: the conditions \eqref{eq:cmasw-dl-validity}
        must hold for the chosen $(a^{swp}, a^{asw})$ pair; otherwise
        the implied dynamics are inadmissible.
\end{enumerate}
\end{validation}

% =====================================================================
\section{Glossary of symbols (paper's notation)}
\begin{tabular}{@{}p{3cm}p{12cm}@{}}
\toprule
$R^{asw}_{t T_0}$       & Forward asset swap spread at $t$ for ASW starting at $T_0$ \\
$R^{swp}_t$             & Forward swap rate at $t$ \\
$B_t$                   & Reference bond price process \\
$B^{\text{risk-free}}_t$ & Hypothetical risk-free version of the same bond \\
$D_{tT}$                & Risk-free DF \\
$A_t$                   & Risk-free annuity over the schedule \\
$T_0$                   & Fixing date \\
$T_p$                   & Payment date, $T_p \ge T_0$ \\
$T_1, \ldots, T_n$      & Bond / annuity schedule dates \\
$yf(T_{i-1}, T_i)$      & Year fraction (often denoted $\alpha_i$ in the paper) \\
$N_t$                   & Numeraire process (paper picks $N = A$) \\
$\alpha, \beta_U$       & Linear-model coefficients \\
$\sigma^{swp}, \sigma^{asw}$ & DL vols of the swap rate / ASW spread \\
$a^{swp}, a^{asw}$      & DL displacements \\
$\rho$                  & Instantaneous correlation \\
$W^{swp}, W^{asw}$      & Driving Brownian motions \\
$CC$                    & Convexity correction (paper's eq.~(3)) \\
\bottomrule
\end{tabular}

% =====================================================================
\begin{todobox}
\begin{itemize}[noitemsep]
  \item Reproduce Table 2 in full (lognormal grid) and Table 3 in
        full (DL slope sensitivity) using \eqref{eq:cmasw-cc-lognormal}
        and \eqref{eq:cmasw-cross-exp}.
  \item Schedule used in the paper's example: bond schedule from
        Tab.~4 (not transcribed here); recover from paper if a full
        end-to-end reproduction is needed.
  \item Discount curve from Tab.~5: not transcribed; the linear-model
        coefficients $\alpha, \beta_U$ for the canonical case must
        be derived from the same curve to reproduce Table 2.
  \item Multi-curve generalisation: the paper notes (end of \S5) that
        formula \eqref{eq:cmasw-cc-prop} extends naturally to a
        multi-curve framework where the swap-rate projection and
        discount are independent. Not in scope for first-pass
        validation but worth bookmarking.
\end{itemize}
\end{todobox}

\end{document}
